master thesis

### 2018-03-20 Paper - Latex/Paper - Skizze - v4.tex
Paper - Results - Biological viwe - update Figure and text for it

      %---------------------------------------------------------------------------------------------------
      \subsubsection{Data artifacts}
        At this point we also found out that there are some nodes with only one child node (55700 nodes). \\
        These are both, the most nodes are right in front of a leaf, as well as some nodes are deep in the 
          tree (3956 with height $>2$). They are probably a result from the fact that taxonomic information 
          has been incorporated into a phylogeny. \\
        Some examples:
        \begin{itemize}
          \item Nephroselmidophyceae: (class) \\
            https://tree.opentreeoflife.org/opentree/argus/ottol@1038762
          \item Phrynocrinidae: (family) \\
            https://tree.opentreeoflife.org/opentree/argus/ottol@3647979
          \item Elaeocarpus sylvestris: \\
            https://tree.opentreeoflife.org/opentree/argus/opentree9.1@ott166969
        \end{itemize}

@@

      \begin{figure}[h!]
        \centering
        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.85\textwidth]{Figures/ChordataParasites.png}
        \caption{Parasites of Phylum: Chordata}
        \label{fig:ChordataParasites}
      \end{figure}

      We mapped the few parasitic spezies in a rough taxonomy (see Figure \ref{fig:ChordataParasites}): \\
      Known parasitic birds belong to the order Sauria. Here we know from Rothschild  here there are 
        breeding parasites, like the cuckoo and clepto-parasites as the skuas \cite{Rothschild1957}. We
        got 6 input parasites from GloBI and there are no predictions: A woodpecker - Sphyrapicus varius
        and a duck - Aix sponsa, a cow bird - Molothrus ater known as broodparasite and some others. \\
        % Other birds: Columba livia, Nestor meridionalis, Sphyrapicus varius \\
        % Snake: Storeria dekayi (probably caused by wrong input data.)
      % \begin{itemize}
      %   \item Order Cypriniformes (7): carp-type without family.
      %   \item Order Acanthomorphata(3):, one slime fish (family Blenniidae) and two others without family
      %   \item Order Anura (1): a toad (Family Bufonidae) - there exists some parasitic species in here, 
      %     they eat fin or pieces of larger fish.
      %   \item Order Siluriformes (1): a catfish (Family Loricariidae) - there exists some parasitic 
      %     species in here.
      % \end{itemize}
      % For the Chordata as parasitic species were predicted in the following orders and families:
      % \begin{itemize}
      %   \item Order Cypriniformes (16), nine predicted parasites.
      %   \item Order Sauria (6), only given input parasites.
      %   \item Order Acanthomorphata(3), only given input parasites.
      %   \item Order Anura (1), only given input parasite.
      %   \item Order Siluriformes (1), only given input parasites.
      % \end{itemize}

>>>>

      %---------------------------------------------------------------------------------------------------
      \subsubsection{Data artifacts}
        At this point we also found out that there are some nodes with only one child node (55,700 nodes). \\
        These are both, the most nodes are right in front of a leaf, as well as some nodes are deep in the 
          tree (3,956 with height $>2$). They are probably a result from the fact that taxonomic information 
          has been incorporated into a phylogeny. \\
        Some examples:
        \begin{itemize}
          \item Nephroselmidophyceae: (class) \\
            https://tree.opentreeoflife.org/opentree/argus/ottol@1038762
          \item Phrynocrinidae: (family) \\
            https://tree.opentreeoflife.org/opentree/argus/ottol@3647979
          \item Elaeocarpus sylvestris: \\
            https://tree.opentreeoflife.org/opentree/argus/opentree9.1@ott166969
        \end{itemize}

@@

      \begin{figure}[h!]
        \centering
        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip, width=0.85\textwidth]{Figures/ChordataParasites.png}
        \caption{Parasites of Phylum: Chordata \\ 
          Input parasites (green) $\rightarrow$ predicted parasites (white $\rightarrow$ green)}
        \label{fig:ChordataParasites}
      \end{figure}
    %---------------------------------------------------------------------------------------------------

      We mapped the few parasitic spezies in a rough taxonomy (see Figure \ref{fig:ChordataParasites}): \\
      Known parasitic birds belong to the order Sauria. Here we know from Rothschild  here there are 
        breeding parasites, like the cuckoo and clepto-parasites as the skuas \cite{Rothschild1957}. We
        got 6 input parasites from GloBI and there are no predictions: A woodpecker - 
        \textit{Sphyrapicus varius} and a duck - \textit{Aix sponsa}, a cow bird - \textit{Molothrus ate} 
        known as broodparasite and some others. \\
      An example of the amplification of mistakes here are the carp. There seems to be a paper from the 
        GloBI concluding: Grass carp (\textit{Ctenopharyngodon idella)} has Pathogen common carp 
        (\textit{Cyprinus carpio})\footnote{
          \hyperlink{https://www.globalbioticinteractions.org/?interactionType=hasParasite&targetTaxon=Cyprinus\%20carpio}
          {https://www.globalbioticinteractions.org/?interactionType=hasParasite\&targetTaxon=Cyprinus\%20carpio}
        }. Since there is hardly any information about free-living, it follows that all siblings are 
        also predicted to be parasitic. \\
        % Other birds: Columba livia, Nestor meridionalis, Sphyrapicus varius \\
        % Snake: Storeria dekayi (probably caused by wrong input data.)
      % \begin{itemize}
      %   \item Order Acanthomorphata(3):, one slime fish (family Blenniidae) and two others without family
      %   \item Order Anura (1): a toad (Family Bufonidae) - there exists some parasitic species in here, 
      %     they eat fin or pieces of larger fish.
      %   \item Order Siluriformes (1): a catfish (Family Loricariidae) - there exists some parasitic 
      %     species in here.
      % \end{itemize}
